%\chapter{Common Elements in the Analysis of High Energy Physics Collision Data}
\chapter{Common Elements in the Search for New Physics}
\label{chap:common_search}

\epigraph{
\textit{Our `Age of Anxiety' is, in great part, the result of trying to do today's jobs with yesterday's tools!}
}{--Marshall McLuhan}
%Our Age of Anxiety is, in great part, the result of trying to do today’s jobs with yesterday’s tools! -- Marshall McLuhan
%Diaper spelled backwards is repaid , think about it. -- Marshall McLuhan

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

There are many ways in which physicists study and analyse the data collected by
the ATLAS detector.
Once the gathered data has been aggregated and the physics objects therein
have been reconstructed (Chapter~\ref{chap:objects}), an analysist has at their fingertips access
to the stuff of high energy particle physics from which they
can test their hypotheses or perform measurements of fundamental quantities.
In the present work, several analyses representing the search for BSM physics
will be discussed in detail.
The details of each of these analyses differ quite a bit, but each follow
a general \textit{analysis strategy} that will be discussed
further in Section~\ref{sec:gen_strategy}.
Physics analyses start with a stated goal in mind; for example,
a measurement of some quantity to a desired level of precision
or, as in the analyses to be presented, a statement about the existence of a new particle or theory of new physics.
The methods by which these statements are to be made are intertwined with, and generally
dictate the initial design of, the overall
analysis strategy and are statistical in nature.
In Section~\ref{sec:stat_hypo} a discussion of the statistical methods used
in the analyses to be presented will be given, highlighting how statements about
new physics are made and how broad-strokes physics conclusions can be drawn from them.
Section~\ref{sec:fakes} follows up on the topic of how one estimates particular sources
of SM backgrounds for which the MC simulation cannot be relied upon to give reasonable
predictions, particularly on those processes that lead to leptons being produced in the detector
that do not originate from the $pp$ hard-scatter processes of interest.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% GENERAL STRATEGY
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{sections/chapter_common_analysis_items_sub/analysis_strategy}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% STATISTICS AND HYPOTHESIS TESTING
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{sections/chapter_common_analysis_items_sub/stats_and_hypo}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% FAKES
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{sections/chapter_common_analysis_items_sub/fakes}
