\chapter{Physics Building Blocks and their Reconstruction}
\label{chap:objects}

\epigraph{\textit{If you can put your five fingers through it it is a gate, if not a door.}}{--Stephen Dedalus, in James Joyce's \textit{Ulysses}}

In order to convert the multitude of electrical signals read out by the subdetectors
of ATLAS as a result of a sucessful trigger (c.f. Section~\ref{sec:tdaq})
into well-defined and meaningful representations of the underlying physics process
that initiated them, at the level required for performing high-quality physics analysis,
several steps of reconstruction and identification must take place.
The physics analyses presented in the current work involve the use of leptons,
jets, and the so-called missing transverse momentum, \ptmiss.
The methods used to deduce the presence of these objects within the ATLAS detector
will be discussed in this chapter.
Section~\ref{sec:tracks_and_vertices} introduces the reconstruction of charged-particle
tracks and $pp$ interaction vertices within the ID, both of which are used as low-level seeds or inputs to the
reconstruction of the high-level physics objects to be discussed in the subsequent
sections.
Section~\ref{sec:leptons} goes on to discuss the reconstruction of the charged leptons
relevant to the current work: electrons and muons.
Sections~\ref{sec:jets} and \ref{sec:flavor_tagging} describe the reconstruction
of jet objects and the identification of jets arising from the decay of heavy-flavor hadrons,
respectively.
Section~\ref{sec:met} then goes on to describe the reconstruction of \ptmiss,
which relies on an accurate description of leptons and jets.
The methods used for reconstructing the leptons and jets are not one hundred percent
accurate: detector information arising due to an electron may leave signatures
similar to those of a jet, for example, and thus spoil their unambiguous description.
Where relevant, in the following we will discuss the methods by which the reconstruction
and identification of the physics objects is made more precise and how high levels
of confidence about their actual presence within the detector are achieved.
Section~\ref{sec:object_ambiguity} will also introduce the notion of high-level
object ambiguity resolution through the use of so-called \textit{overlap removal}
procedures.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% TRACKING AND VERTEXING
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{sections/chapter_object_reco_sub/tracks_and_vertex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% LEPTONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{sections/chapter_object_reco_sub/leptons}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% JETS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{sections/chapter_object_reco_sub/jets}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% FLAVOR TAGGING
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{sections/chapter_object_reco_sub/flavor_tagging}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% MET
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{sections/chapter_object_reco_sub/met}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% OVERLAP REMOVAL
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{sections/chapter_object_reco_sub/object_ambiguity}

%\section{Ambiguity Solving}
