\section{Event Selection and Object Definitions}
\label{sec:stop_event_sel}

In this section, the definitions of the event sample and of the reconstructed
objects used in the analysis are given.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TRIGGER
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Trigger Selection}
\label{sec:stop_trigger}

As described in Section~\ref{sec:stop_final_state}, the $W$-bosons in the three-body
\stopone decays are on-shell and therefore lead to leptons whose kinematics are not
kinematically suppressed.
Each of the leptons is expected to have similar kinematics, given the relatively uncorrelated nature
of their decay, with transverse momenta on average at the scale of $m_W / 2 \sim 40\,\GeV$.
For this reason, the analysis can rely entirely on triggers based on the leptons.
The set of triggers used in the search for $\bWN$ is composed entirely of dilepton triggers,
having online lepton \pT~thresholds of of $10-18$\,GeV.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% OBJECT DEFINITIONS
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Object Definitions}
\label{sec:stop_object_def}

Here we describe the definitions of the leptons and jets used in the search for the
production of \stopone quarks.
The lepton (electron and muon) definitions are given in Table~\ref{tab:stop_lepton_def}
and the jet definitions are given in Table~\ref{tab:stop_jet_def}.
Discussion of the working points for lepton identification and isolation is given in
Section~\ref{sec:leptons}.
That of jets is found in Section~\ref{sec:jets} and \ref{sec:flavor_tagging}, for
jets, generically, and $b$-tagged jets, respectively.

The \pT~requirements of the leptons are such that they be on the plateau of the trigger
efficiency, as described in Section~\ref{sec:gather_data}.
The lepton isolation requirements are rather loose, given that a large contamination of 
fake and non-prompt leptons is not expected as a result of the requirement of two relatively
high-\pT~leptons.
The requirements on the impact parameter quantities $|d_0 / \sigma_{d_0}|$ and $|z_0 \times \sin \theta|$
further ensure that the leptons are likely to be prompt and have originated
from the primary hard-scatter vertex.

\begin{table}[!htb]
    \begin{center}
    \caption{
        Lepton definitions for the 2015+2016 analysis searching for the \stopone quark.
    }
    \label{tab:stop_lepton_def}
        \begin{tabular}{l | c | c | c | c }
        \hline
        \hline
            & \multicolumn{4}{c}{\textbf{Leptons}} \\
        \cline{2-5}
            & \multicolumn{2}{c}{\textbf{Electrons}} & \multicolumn{2}{c}{\textbf{Muons}} \\
        \cline{2-5}
            & \textbf{Baseline} & \textbf{Signal} & \textbf{Baseline} & \textbf{Signal} \\
        \hline
        \pT~requirement [GeV] & $(>10,>10)$ & $(>25,>20)$ & $(>10,>10)$ & $(>25,>20)$ \\
        $|\eta|$ requirement & \multicolumn{2}{c}{$<2.47$} & \multicolumn{2}{c}{$<2.4$} \\
        Identification WP & \texttt{Loose} & \texttt{Medium} & \multicolumn{2}{c}{\texttt{Medium}} \\
        Isolation & \multicolumn{4}{c}{\texttt{GradientLoose}} \\
        $|d_0 / \sigma_{d_0}|$ & $--$ & $<5$ & $--$ & $<3$ \\
        $|z_0 \times \sin \theta|$ [mm] & $--$ & $<0.5$ & $--$ & $<0.5$ \\
        \hline
        \hline
        \end{tabular}
    \end{center}
\end{table}

\begin{table}[!htb]
    \begin{center}
    \caption{
        Jet definitions for the 2015+2016 analysis searching for the \stopone quark.
    }
    \label{tab:stop_jet_def}
        \begin{tabular}{l | c | c}
            \hline
            \hline
                & \textbf{Jets} & \textbf{$b$-tagged Jets} \\
            \hline
            \pT~requirement [GeV] & \multicolumn{2}{c}{$>20$} \\
            $|\eta|$ requirement & $<2.8$ & $<2.4$ \\
            Pileup suppression & \multicolumn{2}{c}{ $\texttt{JVT} > 0.59$ if $\pT<60\,\GeV$~ and $|\eta| < 2.4$} \\
            Flavor-tagging WP & $--$ & $77\%$ \\
            \hline
            \hline
        \end{tabular}
    \end{center}
\end{table}

\subsection{Standard Event Pre-selection}
\label{sec:stop_preselection}

The starting sample of events, referred to as the analysis' \textit{preselection} level,
is defined simply and requires that events satisfy the following basic `data quality' (DQ) requirements:

\begin{itemize}
    \item No issues in any of the ATLAS subsystems were detected when the event was recorded
    \item A primary vertex with at least 2 tracks must be present in the event
    \item No cosmic muons\footnote{A cosmic muon is a reconstructed muon that is not consistent with
        having originated from the primary vertex, and therefore likely to have originated from
        a cosmic ray air shower.
        If a reconstructed muon does not satisfy both $|z_0| < 1$\,mm and $|d_0|<0.2$\,mm, it is considered
        a cosmic muon.} can be in the event
    \item If a poorly reconstructed jet is found in the event, likely to have arisen from stochastic
        noise bursts or issues in the calorimeter system, the event is rejected
\end{itemize}

Additionally, all events entering the analysis must also have two baseline level leptons (c.f. Table~\ref{tab:stop_lepton_def})
which have opposite electric charges, and must have a dilepton invariant mass $m_{\ell \ell}~>~20$\,GeV.
This latter requirement on $m_{\ell\ell}$ removes backgrounds due to low-mass $Z$-boson resonances, such as the $J/\psi$ ($m \sim 5\,\GeV$)
and $\Upsilon$ ($m \sim 11\,\GeV$) mesons. The complete preselection is summarized in Table~\ref{tab:stop_preselection}.

\begin{table}[!htb]
    \begin{center}
        \caption{
            Preselection summary for the 2015+2016 analysis searching for the \stopone quark.
            Signal level object requirements (Table~\ref{tab:stop_lepton_def} and \ref{tab:stop_jet_def}), as well as trigger requirements,
            are applied to the sample of events satisfying these requirements.
        }
        \label{tab:stop_preselection}
        \begin{tabular}{l|c| c}
            \hline
            \hline
            \textbf{Selection} & \textbf{SF Preselection} & \textbf{DF Preselection} \\
            \hline
            Lepton multiplicity & \multicolumn{2}{c}{$==2$ signal leptons} \\
            Dilepton flavor & $ee$ or $\mu \mu$ & $e\mu$ or $\mu e$ \\
            DQ requirements & \multicolumn{2}{c}{satisfied} \\
            Dilepton charge requirement & \multicolumn{2}{c}{opposite charge (OS)} \\
            Dilepton invariant mass, $m_{\ell\ell}$ [GeV] & \multicolumn{2}{c}{$>20$} \\
            \hline
            \hline
        \end{tabular}
    \end{center}
\end{table}
